### 2016-03-17 ch03-lrm/smoothingRMSdecrease.tex
Clean up in CH03

To distinguish the part of the measured impulse response where the actual impulse response dominates from the part where the noise dominates, the estimated
%measured
 impulse response $\hat{g}_\mathrm{poly}$ is split into smaller segments. One can then gradually determine whether these segments are noise or the actual impulse response.

>>>>

To distinguish the part of the measured impulse response where the actual impulse response dominates from the part where the noise dominates, the estimated impulse response $\hat{g}_\mathrm{poly}$ is split into smaller segments. 
One can then gradually determine whether these segments are noise or the actual impulse response.
